---
title: "Analysis of parent survey"
author: "Lorenz Leuenberger"
date: "`r date()`"
title-block-banner: "#e4003c"
format: 
  html:
    page-layout: full
    toc: true
    number-sections: false
    code-fold: show
    code-tools: true
    embed-resources: true
---

# Working environment and software
## Directory

The folder (parent-survey) for the analysis of the parent survey on the shortage of pediatric primary care has the following structure:

- data
    - raw
    - processed

- R-and-qmd scripts
    - final
    - old

- output
    - figures
    - tables
    
There are 3 R-Quarto files for the analysis:

- 00_data-cleaning.qmd: Clean raw questionnaire data from REDCap with R code provided by REDCap. To name and annotate variables.
- 01_descriptive-analysis.qmd: Descriptive statistics of all questions of the questionnaire.
- 02_data-analysis.qmd: Analysis and documentation for manuscript about having a pediatrician.
- 03_data-analysis.qmd: Analysis and documentation for manuscript about parental expectations and satisfaction.


## Software

Load packages

```{r}
#| output: false
#| warning: false
#| message: false

#Libraries

library(tidyverse)
library(readxl)
library(here)
library(gtsummary)
library(samplingbook)
library(cowplot)
library(ggplot2)
library(broom)
library(cobalt)
library(ggtext)
library(ggrepel)
library(forcats)
library(unibeCols)
library(viridis)
library(scales)
library(DataExplorer)
library(survey)
library(srvyr)
library(DescTools)
library(summarytools)
library(sf)
library(bfsMaps)
options(bfsMaps.base="C:/Program Files/R/bfsMaps/ThemaKart/2023_GEOM_TK")

```


Functions

```{r}
ggtext_size <- function(base_size, ratio = 1) {
  ratio * base_size / ggplot2::.pt
}

```


# Data preparation

We already have the data ready from the first manuscript.
There, we weighted the study population using survey design weights and inverse probability weights (responders vs nonresponders).

## Import data


```{r}
#| warning: false
#| output: false

# survey
load(here("data", "processed", "data_included.RData"))


```


## Factor variables

```{r}

data_included <- data_included |> 
  mutate(fte_category_18 = factor(fte_category_18,
                                  levels = c(">0.83", "0.50-0.83", "<0.50")))

```


## Survey object

```{r}

parent_survey_design <- svydesign(id =~1, data = data_included, weights = ~combined_weight_rescaled, strata = ~stratum_sample_fso_surveyed)

```

# Study population characteristics

Complete responses

```{r}
data_included |> select(parent_questionnaire_complete) |> tbl_summary()

```




## Table 1: Characteristics

```{r}
#| warning: false


data_included |> select(role_responder, age_responder, age_group_responder, mother_language_responder_group, 
               sex_letter_child_fso, age_letter_child, age_group_letter_child, child_rank, disease_letter_child, pediatric_care_letter_child,
               living_with_other_parent, nationality_parents, number_children_household_fso_cat, highest_parental_education_group, household_work, household_working_percentage,
               language_region, major_region, urbanization, swiss_sep_2) |> plot_histogram()

data_included |> select(role_responder, age_responder, age_group_responder,mother_language_responder_group, 
               sex_letter_child_fso, age_letter_child, age_group_letter_child, child_rank, disease_letter_child, pediatric_care_letter_child,
               living_with_other_parent, nationality_parents, number_children_household_fso_cat,
               highest_parental_education_group, household_work, household_working_percentage_double, household_working_percentage_single, swiss_sep_2, swiss_sep_2_quintile,
               major_region, urbanization, fte_category_18) |> 
  tbl_summary(type = list(all_continuous() ~ "continuous2",
                          all_dichotomous() ~ "categorical"),
              statistic = list(all_categorical() ~ "{n} ({p})",
                               "age_responder" ~ "{median} [{p25}, {p75}]",
                               "age_letter_child" ~ "{median} [{p25}, {p75}]",
                               "household_working_percentage_double" ~ "{median} [{p25}, {p75}]",
                               "household_working_percentage_single" ~ "{median} [{p25}, {p75}]",
                               "swiss_sep_2" ~ "{mean} ({sd})"),
                 missing_stat = "{N_miss} ({p_miss})",
digits = all_categorical() ~ 0)


parent_survey_design |> as_survey() |> 
  select(role_responder, age_responder, age_group_responder,mother_language_responder_group, 
               sex_letter_child_fso, age_letter_child, age_group_letter_child, child_rank, disease_letter_child, pediatric_care_letter_child,
               living_with_other_parent, nationality_parents, number_children_household_fso_cat,
               highest_parental_education_group, household_work, household_working_percentage_double, household_working_percentage_single, swiss_sep_2, swiss_sep_2_quintile,
               major_region, urbanization, fte_category_18) |> 
  tbl_svysummary(missing = "always",
                 type = list(all_dichotomous() ~ "categorical",
                             all_continuous() ~ "continuous2"),
                 statistic = list(all_categorical() ~ "{n_unweighted} ({p})",
                               "age_responder" ~ "{median} [{p25}, {p75}]",
                               "age_letter_child" ~ "{median} [{p25}, {p75}]",
                               "household_working_percentage_double" ~ "{median} [{p25}, {p75}]",
                               "household_working_percentage_single" ~ "{median} [{p25}, {p75}]",
                               "swiss_sep_2" ~ "{mean} ({sd})"),
                 digits = list(everything() ~ 0),
                 missing_stat = "{N_miss} ({p_miss})")

```



# Characteristics of pediatric primary care

## Table 2: by FTE

```{r}
#| warning: false

data_included |> 
  filter(pediatric_care_letter_child == "Kinderarzt") |> 
  select(fte_category_18) |> 
  tbl_summary()

parent_survey_design |> as_survey() |> 
  filter(pediatric_care_letter_child == "Kinderarzt") |> 
  select(fte_category_18) |> 
  tbl_svysummary(missing = "always",
                 type = list(all_dichotomous() ~ "categorical",
                             all_continuous() ~ "continuous2"),
                 statistic = list(all_categorical() ~ "{n_unweighted} ({p})",
                                  all_continuous() ~ "{median} [{p25}, {p75}]"),
                 digits = list(everything() ~ 0),
                 missing_stat = "{N_miss} ({p_miss})")

data_included |> 
  filter(pediatric_care_letter_child == "Kinderarzt") |> 
  select(duration_until_check_up_non_urgent, duration_until_emergency, intro_too_long_duration_until_consultation,
         waiting_time, intro_too_long_waiting_time_consultations,
         duration_check_up, duration_non_urgent, duration_emergency, intro_too_long_duration_consultations) |> 
  tbl_summary()

parent_survey_design |> as_survey() |> 
  filter(pediatric_care_letter_child == "Kinderarzt") |> 
  select(fte_category_18,
         duration_until_check_up_non_urgent, duration_until_emergency, intro_too_long_duration_until_consultation,
         waiting_time, intro_too_long_waiting_time_consultations,
         duration_check_up, duration_non_urgent, duration_emergency, intro_too_long_duration_consultations) |> 
  tbl_svysummary(by = "fte_category_18",
                 missing = "always",
                 type = list(all_dichotomous() ~ "categorical",
                             all_continuous() ~ "continuous2"),
                 statistic = list(all_categorical() ~ "{n_unweighted} ({p})",
                                  all_continuous() ~ "{median} [{p25}, {p75}]"),
                 digits = list(everything() ~ 0),
                 missing_stat = "{N_miss} ({p_miss})") |> 
  add_overall() |> 
  add_ci(pattern = "{stat} [{ci}]",
         method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 0, scale = 100)) |> 
  add_p()

```





## Table 3: for GPs

```{r}
#| warning: false

data_included |> 
  filter(pediatric_care_letter_child == "Hausarzt") |> 
  select(duration_until_check_up_non_urgent, duration_until_emergency, intro_too_long_duration_until_consultation,
         waiting_time, intro_too_long_waiting_time_consultations,
         duration_check_up, duration_non_urgent, duration_emergency, intro_too_long_duration_consultations) |> 
  tbl_summary()

parent_survey_design |> as_survey() |> 
  filter(pediatric_care_letter_child == "Hausarzt") |> 
  select(duration_until_check_up_non_urgent, duration_until_emergency, intro_too_long_duration_until_consultation,
         waiting_time, intro_too_long_waiting_time_consultations,
         duration_check_up, duration_non_urgent, duration_emergency, intro_too_long_duration_consultations) |> 
  tbl_svysummary(missing = "always",
                 type = list(all_dichotomous() ~ "categorical",
                             all_continuous() ~ "continuous2"),
                 statistic = list(all_categorical() ~ "{n_unweighted} ({p})",
                                  all_continuous() ~ "{median} [{p25}, {p75}]"),
                 digits = list(everything() ~ 0),
                 missing_stat = "{N_miss} ({p_miss})") |> 
  add_ci(pattern = "{stat} [{ci}]",
         method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 0, scale = 100))

```


# Expectations towards physicians and practices

## Figure 2: Important characteristics

```{r}
#| warning: false

data_included |> 
  select(important_doctor_pediatrician, important_doctor_experience, important_doctor_complementary, important_doctor_mother_language, important_doctor_time, important_doctor_involves_parent) |> 
  tbl_summary(
    missing = "always",
    stat = all_categorical() ~ "{n} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    )
  
parent_survey_design |> as_survey() |> 
  select(important_doctor_pediatrician, important_doctor_experience, important_doctor_complementary, important_doctor_mother_language, important_doctor_time, important_doctor_involves_parent) |> 
  tbl_svysummary(
    missing = "always",
    stat = all_categorical() ~ "{n_unweighted} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 1, scale = 100))

tbl_important_doctor <- parent_survey_design |> as_survey() |> 
  select(important_doctor_pediatrician, important_doctor_experience, important_doctor_complementary, important_doctor_mother_language, important_doctor_time, important_doctor_involves_parent) |> 
  tbl_svysummary(
    missing = "always",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))


data_included |> 
  select(important_practice_close, important_practice_open_weekday, important_practice_free_appointments, important_practice_emergencies_same_day, important_practice_short_waiting, important_practice_same_doctor) |> 
  tbl_summary(
    missing = "always",
    stat = all_categorical() ~ "{n} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    )

parent_survey_design |> as_survey() |> 
  select(important_practice_close, important_practice_open_weekday, important_practice_free_appointments, important_practice_emergencies_same_day, important_practice_short_waiting, important_practice_same_doctor) |> 
  tbl_svysummary(
    missing = "always",
    stat = all_categorical() ~ "{n_unweighted} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 0, scale = 100))


tbl_important_practice <- parent_survey_design |> as_survey() |> 
  select(important_practice_close, important_practice_open_weekday, important_practice_free_appointments, important_practice_emergencies_same_day, important_practice_short_waiting, important_practice_same_doctor) |> 
  tbl_svysummary(
    missing = "always",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))



```


```{r}
#| warning: false

data_important_doctor <- tbl_important_doctor |> 
  as_tibble() |> 
  filter(`**Characteristic**` != "Unknown") |> 
  transmute(
    Factor = `**Characteristic**`,
    n_perc = `**N = 8,651**`,
    ci_text = `**95% CI**`
  ) |> 
  mutate(
    yes_count = as.numeric(str_remove_all(str_extract(n_perc, "^[0-9,]+"), ",")),
    yes_proportion = str_extract(n_perc, "\\(([^\\)]+)\\)") %>%
                     str_remove_all("[^0-9\\.]") %>%
                     as.numeric() / 100,
    yes_ci_lower = str_extract(ci_text, "^[0-9\\.]+") %>% as.numeric() / 100,
    yes_ci_upper = str_extract(ci_text, "[0-9\\.]+(?=%?$)") %>% as.numeric() / 100) |> 
  select(Factor, yes_count, yes_proportion, yes_ci_lower, yes_ci_upper)


data_important_doctor <- data_important_doctor |> 
  mutate(Factor = factor(Factor, levels = c("important_doctor_complementary", "important_doctor_mother_language", "important_doctor_experience", "important_doctor_involves_parent",  "important_doctor_pediatrician", "important_doctor_time"), labels = c("Complementary medicine", "Mother tongue", "Experience", "Shared decision making", "Trained pediatrician", "Enough time")))

plot_important_doctor <- data_important_doctor |>
  ggplot(aes(y = Factor, x = yes_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbarh(aes(xmin = yes_ci_lower, xmax = yes_ci_upper), height = 0.25)+
  geom_text(aes(x = yes_proportion/2, label = paste0(round(yes_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(9))+
  scale_x_continuous(labels = percent, limits = c(0, 1))+
  theme_minimal()+
  ggtitle("Doctor's characteristics")+
  xlab("Important to parents (%)")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color = "black"),
        plot.title = element_text(size = 12, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"))

plot_important_doctor


data_important_practice <- tbl_important_practice |> 
  as_tibble() |> 
  filter(`**Characteristic**` != "Unknown") |> 
  transmute(
    Factor = `**Characteristic**`,
    n_perc = `**N = 8,651**`,
    ci_text = `**95% CI**`
  ) |> 
  mutate(
    yes_count = as.numeric(str_remove_all(str_extract(n_perc, "^[0-9,]+"), ",")),
    yes_proportion = str_extract(n_perc, "\\(([^\\)]+)\\)") %>%
                     str_remove_all("[^0-9\\.]") %>%
                     as.numeric() / 100,
    yes_ci_lower = str_extract(ci_text, "^[0-9\\.]+") %>% as.numeric() / 100,
    yes_ci_upper = str_extract(ci_text, "[0-9\\.]+(?=%?$)") %>% as.numeric() / 100) |> 
  select(Factor, yes_count, yes_proportion, yes_ci_lower, yes_ci_upper)


data_important_practice <- data_important_practice |> 
  mutate(Factor = factor(Factor, levels = c("important_practice_free_appointments", "important_practice_short_waiting", "important_practice_same_doctor", "important_practice_open_weekday",  "important_practice_close", "important_practice_emergencies_same_day"), labels = c("Many free appointments", "Short waiting times", "Same doctor", "Open all weekdays", "Close to home", "Emergencies on the same day")))

plot_important_practice <- data_important_practice |>
  ggplot(aes(y = Factor, x = yes_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbarh(aes(xmin = yes_ci_lower, xmax = yes_ci_upper), height = 0.25)+
  geom_text(aes(x = yes_proportion/2, label = paste0(round(yes_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(9))+
  scale_x_continuous(labels = percent, limits = c(0, 1))+
  theme_minimal()+
  ggtitle("Practice's characteristics")+
  xlab("Important to parents (%)")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color = "black"),
        plot.title = element_text(size = 12, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"))

plot_important_practice

plot_figure_expectations <- plot_grid(plot_important_doctor+theme(axis.title.x = element_blank()),
                           plot_important_practice,
                           ncol = 1,
                           align = "hv")

plot_figure_expectations

ggsave(filename=file.path(here("output","figures","plot_figure_expectations.svg")),plot_figure_expectations,device=svg,units="cm", height=10, width=18)

```



# Satisfaction

```{r}
#| warning: false

parent_survey_design |> 
  as_survey() |> 
  select(satisfaction_doctor, satisfaction_practice) |> 
  tbl_svysummary(
    missing = "always",
    type = all_dichotomous() ~ "categorical",
    statistic = all_categorical() ~ "{n_unweighted} ({p}%)",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci()

```


## Figure 1: By canton and pediatrician vs GP

```{r}
#| warning: false

tbl_satisfaction_doctor_canton <- parent_survey_design |> 
  as_survey() |> 
  select(satisfaction_doctor, canton_recoded) |> 
  tbl_svysummary(
    by = "canton_recoded",
    missing = "always",
    type = all_dichotomous() ~ "categorical",
    statistic = all_categorical() ~ "{n_unweighted} ({p}%)",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         pattern = "{stat} [{ci}]",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))

tbl_satisfaction_doctor_canton


tbl_satisfaction_doctor_canton <- tbl_satisfaction_doctor_canton |> 
  as_tibble() |> 
  rename("AG" = 2, "AI/AR" = 3, "BE" = 4, "BL" = 5, "BS" = 6, "FR" = 7, "GE" = 8, "GL/GR" = 9, "JU" = 10, "LU" = 11, "NE" = 12, "NW/OW/UR" = 13, "SG" = 14, "SH" = 15, "SO" = 16, "SZ" = 17, "TG" = 18, "TI" = 19, "VD" = 20, "VS" = 21, "ZG" = 22, "ZH" = 23)|> 
  filter(`**Characteristic**` == "Zufrieden") |>
  pivot_longer(cols = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23), names_to = "canton_recoded") |> 
  mutate(
    Zufrieden_doctor_n = str_extract(value, "^[0-9,]+") |> str_remove_all(",") |> as.numeric(),
    Zufrieden_doctor_proportion = str_extract(value, "(?<=\\()[0-9\\.]+(?=%)") |> as.numeric() / 100,
    Zufrieden_doctor_ci_lower   = str_extract(value, "(?<=\\[)[0-9\\.]+") |> as.numeric() / 100,
    Zufrieden_doctor_ci_upper   = str_extract(value, "(?<=, )[0-9\\.]+") |> as.numeric() / 100) |> 
  select(canton_recoded, Zufrieden_doctor_n, Zufrieden_doctor_proportion, Zufrieden_doctor_ci_lower, Zufrieden_doctor_ci_upper)


```


```{r}
#| warning: false

map_cantons_sf <- GetMap("kant.map") |> 
  st_as_sf()

map_cantons_recoded_sf <- map_cantons_sf |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "AR" | idx == "AI") %>%
              summarise(idx = "AI/AR",
                        name = "AI/AR",
                        geometry = st_union(geometry))) |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "GL" | idx == "GR") %>%
              summarise(idx = "GL/GR",
                        name = "GL/GR",
                        geometry = st_union(geometry))) |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "NW" | idx == "OW" | idx == "UR") %>%
              summarise(idx = "NW/OW/UR",
                        name = "NW/OW/UR",
                        geometry = st_union(geometry))) |> 
  filter(idx != "AR" & idx != "AI" & idx != "GL" & idx != "GR" & idx != "NW" & idx != "OW" & idx != "UR")

lakes_sf <- GetMap("see1.map") |> 
  st_as_sf()


map_cantons_recoded_sf <- map_cantons_recoded_sf %>%
  left_join(tbl_satisfaction_doctor_canton, by = c("idx" = "canton_recoded")) |> 
  bind_cols(st_coordinates(st_centroid(map_cantons_recoded_sf)))

plot_satisfaction_doctor_canton_recoded <- ggplot(data = map_cantons_recoded_sf) +
  geom_sf(data = lakes_sf, fill = "lightblue", color = NA )+
  geom_sf(aes(fill = Zufrieden_doctor_proportion), color = "black") +
  scale_fill_gradient2(high = unibeIce(), mid = unibeIce(), low = unibeRed(), midpoint = 0.95, breaks = c(0.75, 0.80, 0.85, 0.90, 0.95, 1.0), labels = percent(c(0.75, 0.80, 0.85, 0.90, 0.95, 1.0)), limits = c(0.75, 1.0),)+
  geom_text_repel(mapping = aes(x = ifelse(idx == "VD", X - 7000,
                                    ifelse(idx == "FR", X + 5000,
                                    ifelse(idx == "AG", X + 5000,
                                    ifelse(idx == "NW/OW/UR", X + 10000, X)))),
                                y = ifelse(idx == "FR", Y + 10000,
                                    ifelse(idx == "VD", Y + 5000,
                                    ifelse(idx == "BS", Y + 10000,
                                    ifelse(idx == "SG", Y - 5000,
                                    ifelse(idx == "GE", Y -15000,
                                    ifelse(idx == "TI", Y + 4000, Y)))))), label = ifelse(is.na(Zufrieden_doctor_proportion), "NA", paste0(round(Zufrieden_doctor_proportion*100, 0), "%"))), bg.color = "black", bg.r = 0.1, size = ggtext_size(8), color = "white", force = 0.001, force_pull = 10000)+
  labs(fill = "Satisfaction (%) with child's doctor")+
  theme_minimal()+
  theme(
    plot.title = element_text(size = 8, face = "bold"),
    plot.title.position = "plot",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(family = "Arial", size = 8, colour = "black"),
    legend.title = element_text(family = "Arial", size = 8, colour = "black"),
    legend.box.margin = margin(l=0, b=0, r=0, t=-0.5, unit = "cm"),
    legend.key.width = unit(1, "cm"),
    legend.key.height = unit(0.3, "cm"),
    legend.box.spacing = unit(0, "pt"),
    plot.margin = margin(l=0, b=0, r=0, t=0, unit = "cm")) +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5))

plot_satisfaction_doctor_canton_recoded

ggsave(filename=file.path(here("output","figures","plot_satisfaction_doctor_canton_recoded.svg")),plot_satisfaction_doctor_canton_recoded,device=svg,units="cm", height=12, width=18)

```




```{r}
#| warning: false

tbl_satisfaction_practice_canton <- parent_survey_design |> 
  as_survey() |> 
  select(satisfaction_practice, canton_recoded) |> 
  tbl_svysummary(
    by = "canton_recoded",
    missing = "always",
    type = all_dichotomous() ~ "categorical",
    statistic = all_categorical() ~ "{n_unweighted} ({p}%)",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         pattern = "{stat} [{ci}]",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))

tbl_satisfaction_practice_canton


tbl_satisfaction_practice_canton <- tbl_satisfaction_practice_canton |> 
  as_tibble() |> 
  rename("AG" = 2, "AI/AR" = 3, "BE" = 4, "BL" = 5, "BS" = 6, "FR" = 7, "GE" = 8, "GL/GR" = 9, "JU" = 10, "LU" = 11, "NE" = 12, "NW/OW/UR" = 13, "SG" = 14, "SH" = 15, "SO" = 16, "SZ" = 17, "TG" = 18, "TI" = 19, "VD" = 20, "VS" = 21, "ZG" = 22, "ZH" = 23)|> 
  filter(`**Characteristic**` == "Zufrieden") |>
  pivot_longer(cols = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23), names_to = "canton_recoded") |> 
  mutate(
    Zufrieden_practice_n = str_extract(value, "^[0-9,]+") |> str_remove_all(",") |> as.numeric(),
    Zufrieden_practice_proportion = str_extract(value, "(?<=\\()[0-9\\.]+(?=%)") |> as.numeric() / 100,
    Zufrieden_practice_ci_lower   = str_extract(value, "(?<=\\[)[0-9\\.]+") |> as.numeric() / 100,
    Zufrieden_practice_ci_upper   = str_extract(value, "(?<=, )[0-9\\.]+") |> as.numeric() / 100) |> 
  select(canton_recoded, Zufrieden_practice_n, Zufrieden_practice_proportion, Zufrieden_practice_ci_lower, Zufrieden_practice_ci_upper)


```


```{r}
#| warning: false

map_cantons_sf <- GetMap("kant.map") |> 
  st_as_sf()

map_cantons_recoded_sf <- map_cantons_sf |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "AR" | idx == "AI") %>%
              summarise(idx = "AI/AR",
                        name = "AI/AR",
                        geometry = st_union(geometry))) |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "GL" | idx == "GR") %>%
              summarise(idx = "GL/GR",
                        name = "GL/GR",
                        geometry = st_union(geometry))) |> 
  bind_rows(map_cantons_sf |> 
              filter(idx == "NW" | idx == "OW" | idx == "UR") %>%
              summarise(idx = "NW/OW/UR",
                        name = "NW/OW/UR",
                        geometry = st_union(geometry))) |> 
  filter(idx != "AR" & idx != "AI" & idx != "GL" & idx != "GR" & idx != "NW" & idx != "OW" & idx != "UR")

lakes_sf <- GetMap("see1.map") |> 
  st_as_sf()


map_cantons_recoded_sf <- map_cantons_recoded_sf %>%
  left_join(tbl_satisfaction_practice_canton, by = c("idx" = "canton_recoded")) |> 
  bind_cols(st_coordinates(st_centroid(map_cantons_recoded_sf)))

plot_satisfaction_practice_canton_recoded <- ggplot(data = map_cantons_recoded_sf) +
  geom_sf(data = lakes_sf, fill = "lightblue", color = NA )+
  geom_sf(aes(fill = Zufrieden_practice_proportion), color = "black") +
  scale_fill_gradient2(high = unibeIce(), mid = unibeIce(), low = unibeRed(), midpoint = 0.95, breaks = c(0.75, 0.80, 0.85, 0.90, 0.95, 1.0), labels = percent(c(0.75, 0.80, 0.85, 0.90, 0.95, 1.0)), limits = c(0.75, 1.0),)+
  geom_text_repel(mapping = aes(x = ifelse(idx == "VD", X - 7000,
                                    ifelse(idx == "FR", X + 5000,
                                    ifelse(idx == "AG", X + 5000,
                                    ifelse(idx == "NW/OW/UR", X + 10000, X)))),
                                y = ifelse(idx == "FR", Y + 10000,
                                    ifelse(idx == "VD", Y + 5000,
                                    ifelse(idx == "BS", Y + 10000,
                                    ifelse(idx == "SG", Y - 5000,
                                    ifelse(idx == "GE", Y -15000,
                                    ifelse(idx == "TI", Y + 4000, Y)))))), label = ifelse(is.na(Zufrieden_practice_proportion), "NA", paste0(round(Zufrieden_practice_proportion*100, 0), "%"))), bg.color = "black", bg.r = 0.1, size = ggtext_size(8), color = "white", force = 0.001, force_pull = 10000)+
  labs(fill = "Satisfaction (%) with child's practice")+
  theme_minimal()+
  theme(
    plot.title = element_text(size = 8, face = "bold"),
    plot.title.position = "plot",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(family = "Arial", size = 8, colour = "black"),
    legend.title = element_text(family = "Arial", size = 8, colour = "black"),
    legend.box.margin = margin(l=0, b=0, r=0, t=-0.5, unit = "cm"),
    legend.key.width = unit(1, "cm"),
    legend.key.height = unit(0.3, "cm"),
    legend.box.spacing = unit(0, "pt"),
    plot.margin = margin(l=0, b=0, r=0, t=0, unit = "cm")) +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5))

plot_satisfaction_practice_canton_recoded

ggsave(filename=file.path(here("output","figures","plot_satisfaction_practice_canton_recoded.svg")),plot_satisfaction_practice_canton_recoded,device=svg,units="cm", height=12, width=18)

```

```{r}
#| warning: false

tbl_satisfaction_doctor_GP_ped <- parent_survey_design |> 
  as_survey() |> 
  filter(pediatric_care_letter_child == "Kinderarzt" | pediatric_care_letter_child == "Hausarzt") |> 
  select(satisfaction_doctor, pediatric_care_letter_child) |> 
  tbl_svysummary(
    by = "pediatric_care_letter_child",
    missing = "always",
    type = all_dichotomous() ~ "categorical",
    statistic = all_categorical() ~ "{n_unweighted} ({p}%)",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         pattern = "{stat} [{ci}]",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))

tbl_satisfaction_doctor_GP_ped


tbl_satisfaction_doctor_GP_ped <- tbl_satisfaction_doctor_GP_ped |> 
  as_tibble() |> 
  rename("Pediatrician" = 2, "General practitioner" = 3)|> 
  filter(`**Characteristic**` == "Zufrieden") |>
  pivot_longer(cols = c(2,3), names_to = "pediatric_care") |> 
  mutate(
    Zufrieden_doctor_n = str_extract(value, "^[0-9,]+") |> str_remove_all(",") |> as.numeric(),
    Zufrieden_doctor_proportion = str_extract(value, "(?<=\\()[0-9\\.]+(?=%)") |> as.numeric() / 100,
    Zufrieden_doctor_ci_lower   = str_extract(value, "(?<=\\[)[0-9\\.]+") |> as.numeric() / 100,
    Zufrieden_doctor_ci_upper   = str_extract(value, "(?<=, )[0-9\\.]+") |> as.numeric() / 100) |> 
  select(pediatric_care, Zufrieden_doctor_n, Zufrieden_doctor_proportion, Zufrieden_doctor_ci_lower, Zufrieden_doctor_ci_upper)




tbl_satisfaction_practice_GP_ped <- parent_survey_design |> 
  as_survey() |> 
  filter(pediatric_care_letter_child == "Kinderarzt" | pediatric_care_letter_child == "Hausarzt") |> 
  select(satisfaction_practice, pediatric_care_letter_child) |> 
  tbl_svysummary(
    by = "pediatric_care_letter_child",
    missing = "always",
    type = all_dichotomous() ~ "categorical",
    statistic = all_categorical() ~ "{n_unweighted} ({p}%)",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         pattern = "{stat} [{ci}]",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))

tbl_satisfaction_practice_GP_ped


tbl_satisfaction_practice_GP_ped <- tbl_satisfaction_practice_GP_ped |> 
  as_tibble() |> 
  rename("Pediatric practice" = 2, "General practice" = 3)|> 
  filter(`**Characteristic**` == "Zufrieden") |>
  pivot_longer(cols = c(2,3), names_to = "pediatric_care") |> 
  mutate(
    Zufrieden_practice_n = str_extract(value, "^[0-9,]+") |> str_remove_all(",") |> as.numeric(),
    Zufrieden_practice_proportion = str_extract(value, "(?<=\\()[0-9\\.]+(?=%)") |> as.numeric() / 100,
    Zufrieden_practice_ci_lower   = str_extract(value, "(?<=\\[)[0-9\\.]+") |> as.numeric() / 100,
    Zufrieden_practice_ci_upper   = str_extract(value, "(?<=, )[0-9\\.]+") |> as.numeric() / 100) |> 
  select(pediatric_care, Zufrieden_practice_n, Zufrieden_practice_proportion, Zufrieden_practice_ci_lower, Zufrieden_practice_ci_upper)

```


```{r}
#| warning: false

plot_satisfaction_doctor <- tbl_satisfaction_doctor_GP_ped |>
  ggplot(aes(y = pediatric_care, x = Zufrieden_doctor_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbarh(aes(xmin = Zufrieden_doctor_ci_lower, xmax = Zufrieden_doctor_ci_upper), height = 0.25)+
  geom_text(aes(x = Zufrieden_doctor_proportion/2, label = paste0(round(Zufrieden_doctor_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(7))+
  scale_x_continuous(labels = percent, limits = c(0, 1))+
  theme_minimal()+
  xlab("Satisfaction (%) with child's doctor")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(size = 8, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        axis.title.x = element_text(size = 8, color = "black"))

plot_satisfaction_doctor



plot_satisfaction_practice <- tbl_satisfaction_practice_GP_ped |>
  ggplot(aes(y = pediatric_care, x = Zufrieden_practice_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbarh(aes(xmin = Zufrieden_practice_ci_lower, xmax = Zufrieden_practice_ci_upper), height = 0.25)+
  geom_text(aes(x = Zufrieden_practice_proportion/2, label = paste0(round(Zufrieden_practice_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(7))+
  scale_x_continuous(labels = percent, limits = c(0, 1))+
  theme_minimal()+
  xlab("Satisfaction (%) with child's practice")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(size = 8, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 8, color = "black"),
        axis.title.x = element_text(size = 8, color = "black"))

plot_satisfaction_practice


```


Figure 2

```{r}
#| warning: false

figure_canton_satisfaction <- plot_grid(plot_satisfaction_doctor_canton_recoded, plot_satisfaction_practice_canton_recoded,
                                        ncol = 2)


figure_satisfaction_GP_ped <- plot_grid(plot_satisfaction_doctor, plot_satisfaction_practice,
                                        ncol = 2)

figure_2 <- plot_grid(figure_canton_satisfaction,
                      figure_satisfaction_GP_ped,
                      ncol = 1,
                      rel_heights = c(1, 0.3))

figure_2


ggsave(filename=file.path(here("output","figures","figure_satisfaction.svg")),figure_2,device=svg,units="cm", height=10, width=18)

```



## Table 2: Regression factors satisfaction

```{r}
#| warning: false

data_included <- data_included |> 
  mutate(satisfaction_doctor_recoded = case_when(satisfaction_doctor == "Zufrieden" ~ 1,
                                              satisfaction_doctor == "Unzufrieden" ~ 0,
                                              TRUE ~ NA))

parent_survey_design <- svydesign(id =~1, data = data_included, weights = ~combined_weight_rescaled, strata = ~stratum_sample_fso_surveyed)

```


### Univariable


Sex

```{r}
#| warning: false

model_1a <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso, family = quasibinomial(), design = parent_survey_design)

plot(model_1a)

summary(model_1a)
cbind(exp(summary(model_1a)$coef[,1]), exp(confint(model_1a)))


```
Age

```{r}
#| warning: false

model_1b.1 <- svyglm(satisfaction_doctor_recoded ~ I(age_letter_child/5), family = quasibinomial(), design = parent_survey_design)

plot(model_1b.1)

summary(model_1b.1)
cbind(exp(summary(model_1b.1)$coef[,1]), exp(confint(model_1b.1)))


data_included <- data_included |> 
  mutate(age_group_letter_child = factor(age_group_letter_child,
                                         levels = c("School (6-11)", "Infancy (0-1)", "Preschool (2-5)", "Early adolescence (12-15)", "Late adolescence (16-17)")))

parent_survey_design <- svydesign(ids = ~1, data = data_included, weights = ~combined_weight_rescaled, strata = ~stratum_sample_fso_surveyed, nest = TRUE)

model_1b.2 <- svyglm(satisfaction_doctor_recoded ~ age_group_letter_child, family = quasibinomial(), design = parent_survey_design)

plot(model_1b.2)

summary(model_1b.2)
cbind(exp(summary(model_1b.2)$coef[,1]), exp(confint(model_1b.2)))

AIC(model_1b.1, model_1b.2)


```


Pediatrician vs GP


```{r}
#| warning: false

model_1c <- svyglm(satisfaction_doctor_recoded ~ pediatric_care_letter_child, family = quasibinomial(), design = parent_survey_design)

plot(model_1c)

summary(model_1c)
cbind(exp(summary(model_1c)$coef[,1]), exp(confint(model_1c)))

```

Parental nationality

```{r}
#| warning: false

model_1e <- svyglm(satisfaction_doctor_recoded ~ nationality_parents, family = quasibinomial(), design = parent_survey_design)

plot(model_1e)

summary(model_1e)
cbind(exp(summary(model_1e)$coef[,1]), exp(confint(model_1e)))

```


Parental education

```{r}

model_1f <- svyglm(satisfaction_doctor_recoded ~ highest_parental_education_group, family = quasibinomial(), design = parent_survey_design)

plot(model_1f)

summary(model_1f)
cbind(exp(summary(model_1f)$coef[,1]), exp(confint(model_1f)))

```

Swiss-SEP


```{r}
#| warning: false

model_1g <- svyglm(satisfaction_doctor_recoded ~ I(swiss_sep_2/10), family = quasibinomial(), design = parent_survey_design)

plot(model_1g)

summary(model_1g)
cbind(exp(summary(model_1g)$coef[,1]), exp(confint(model_1g)))


model_1g.1 <- svyglm(satisfaction_doctor_recoded ~ swiss_sep_2_quintile, family = quasibinomial(), design = parent_survey_design)

plot(model_1g.1)

summary(model_1g.1)
cbind(exp(summary(model_1g.1)$coef[,1]), exp(confint(model_1g.1)))

AIC(model_1g.1, model_1g)

```


Urbanization

```{r}
#| warning: false

model_1j <- svyglm(satisfaction_doctor_recoded ~ urbanization, family = quasibinomial(), design = parent_survey_design)

plot(model_1j)

summary(model_1j)
cbind(exp(summary(model_1j)$coef[,1]), exp(confint(model_1j)))

```

Ftes


```{r}
#| warning: false

data_included |> select(fte_per_1000_0_17) |> pull() |> sd()

model_1i <- svyglm(satisfaction_doctor_recoded ~ I(fte_per_1000_0_17*4), family = quasibinomial(), design = parent_survey_design)

plot(model_1i)

summary(model_1i)
cbind(exp(summary(model_1i)$coef[,1]), exp(confint(model_1i)))

data_included <- data_included |> 
  mutate(fte_category_18 = factor(fte_category_18, levels = c("0.50-0.83", ">0.83", "<0.50")))

parent_survey_design <- svydesign(ids = ~1, data = data_included, weights = ~combined_weight_rescaled, strata = ~stratum_sample_fso_surveyed, nest = TRUE)

model_1i.1 <- svyglm(satisfaction_doctor_recoded ~ fte_category_18, family = quasibinomial(), design = parent_survey_design)

plot(model_1i.1)

summary(model_1i.1)
cbind(exp(summary(model_1i.1)$coef[,1]), exp(confint(model_1i.1)))

AIC(model_1i, model_1i.1)

```

Time to appointment check up non urgent

```{r}
#| warning: false

model_1k <- svyglm(satisfaction_doctor_recoded ~ duration_until_check_up_non_urgent, family = quasibinomial(), design = parent_survey_design)

plot(model_1k)

summary(model_1k)
cbind(exp(summary(model_1k)$coef[,1]), exp(confint(model_1k)))

```

Time to appointment emergency

```{r}
#| warning: false

model_1l <- svyglm(satisfaction_doctor_recoded ~ duration_until_emergency, family = quasibinomial(), design = parent_survey_design)

plot(model_1l)

summary(model_1l)
cbind(exp(summary(model_1l)$coef[,1]), exp(confint(model_1l)))

```



Waiting time

```{r}
#| warning: false

model_1m <- svyglm(satisfaction_doctor_recoded ~ I(waiting_time/5), family = quasibinomial(), design = parent_survey_design)

plot(model_1m)

summary(model_1m)
cbind(exp(summary(model_1m)$coef[,1]), exp(confint(model_1m)))

```

Consultation duration

```{r}
#| warning: false

model_1n <- svyglm(satisfaction_doctor_recoded ~ I(duration_check_up/5), family = quasibinomial(), design = parent_survey_design)

plot(model_1n)

summary(model_1n)
cbind(exp(summary(model_1n)$coef[,1]), exp(confint(model_1n)))

```

```{r}
#| warning: false

model_1o <- svyglm(satisfaction_doctor_recoded ~ I(duration_non_urgent/5), family = quasibinomial(), design = parent_survey_design)

plot(model_1o)

summary(model_1o)
cbind(exp(summary(model_1o)$coef[,1]), exp(confint(model_1o)))

```


```{r}
#| warning: false

model_1p <- svyglm(satisfaction_doctor_recoded ~ I(duration_emergency/5), family = quasibinomial(), design = parent_survey_design)

plot(model_1p)

summary(model_1p)
cbind(exp(summary(model_1p)$coef[,1]), exp(confint(model_1p)))

```


### Multivariable

```{r}
#| warning: false

model_2a <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile + urbanization +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up + duration_non_urgent + duration_emergency, family = quasibinomial(), design = parent_survey_design)

plot(model_2a)

summary(model_2a)
cbind(exp(summary(model_2a)$coef[,1]), exp(confint(model_2a)))


View(tidy(model_2a, conf.int = TRUE, exponentiate = TRUE) %>% 
  mutate(
    aOR_CI = sprintf("%.2f [%.2f–%.2f]", estimate, conf.low, conf.high)
  ) %>%
  select(term, aOR_CI))

data_included |> select(sex_letter_child_fso , age_group_letter_child , pediatric_care_letter_child, nationality_parents , highest_parental_education_group , swiss_sep_2_quintile , urbanization ,  fte_category_18 , duration_until_check_up_non_urgent , duration_until_emergency , waiting_time , duration_check_up , duration_non_urgent , duration_emergency) |>
  drop_na() |> nrow()


```

Drop variables

```{r}
#| warning: false


model_2b <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile + urbanization +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up + duration_non_urgent, family = quasibinomial(), design = parent_survey_design)

plot(model_2b)

summary(model_2b)
cbind(exp(summary(model_2b)$coef[,1]), exp(confint(model_2b)))

glance(model_2a)
glance(model_2b)

anova(model_2a, model_2b)



```

We exclude duration emergency as the model with it is not significantly better than the one without it


```{r}
#| warning: false

model_2c <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile + urbanization +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2c)

summary(model_2c)
cbind(exp(summary(model_2c)$coef[,1]), exp(confint(model_2c)))

glance(model_2b)
glance(model_2c)
anova(model_2b, model_2c)

```

We exclude duration non urgent as the model with it is not significantly better than the one without it


```{r}
#| warning: false

model_2d <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile + urbanization +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time, family = quasibinomial(), design = parent_survey_design)

plot(model_2d)

summary(model_2d)
cbind(exp(summary(model_2d)$coef[,1]), exp(confint(model_2d)))

glance(model_2c)
glance(model_2d)
anova(model_2c, model_2d)

```

We keep duration check up.

```{r}
#| warning: false

model_2e <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile + urbanization +  fte_category_18 + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2e)

summary(model_2e)
cbind(exp(summary(model_2e)$coef[,1]), exp(confint(model_2e)))

glance(model_2c)
glance(model_2e)
anova(model_2c, model_2e)

```

We keep time to checkup consultation.

```{r}
#| warning: false

model_2f <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group + swiss_sep_2_quintile +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2f)

summary(model_2f)
cbind(exp(summary(model_2f)$coef[,1]), exp(confint(model_2f)))

glance(model_2c)
glance(model_2f)
anova(model_2c, model_2f)

```

We drop urbanization.

```{r}
#| warning: false

model_2g <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + highest_parental_education_group +  fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2g)

summary(model_2g)
cbind(exp(summary(model_2g)$coef[,1]), exp(confint(model_2g)))

glance(model_2f)
glance(model_2g)
anova(model_2f, model_2g)

```

We drop Swiss-SEP

```{r}
#| warning: false

model_2h <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + nationality_parents + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2h)

summary(model_2h)
cbind(exp(summary(model_2h)$coef[,1]), exp(confint(model_2h)))

glance(model_2g)
glance(model_2h)
anova(model_2g, model_2h)

```


We drop Education

```{r}
#| warning: false

model_2i <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + age_group_letter_child + pediatric_care_letter_child + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2i)

summary(model_2i)
cbind(exp(summary(model_2i)$coef[,1]), exp(confint(model_2i)))

glance(model_2h)
glance(model_2i)
anova(model_2h, model_2i)

```


We drop nationality

```{r}
#| warning: false

model_2j <- svyglm(satisfaction_doctor_recoded ~ sex_letter_child_fso + pediatric_care_letter_child + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2j)

summary(model_2j)
cbind(exp(summary(model_2j)$coef[,1]), exp(confint(model_2j)))

glance(model_2i)
glance(model_2j)
anova(model_2i, model_2j)

```

We keep age group

```{r}
#| warning: false

model_2k <- svyglm(satisfaction_doctor_recoded ~ age_group_letter_child + pediatric_care_letter_child + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2k)

summary(model_2k)
cbind(exp(summary(model_2k)$coef[,1]), exp(confint(model_2k)))

glance(model_2i)
glance(model_2k)
anova(model_2i, model_2k)

```

We drop sex of child


Re-include variables?

```{r}
#| warning: false

model_2l <- svyglm(satisfaction_doctor_recoded ~ age_group_letter_child + pediatric_care_letter_child + nationality_parents + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2l)

summary(model_2l)
cbind(exp(summary(model_2l)$coef[,1]), exp(confint(model_2l)))

glance(model_2k)
glance(model_2l)
anova(model_2k, model_2l)

```


```{r}
#| warning: false

model_2m <- svyglm(satisfaction_doctor_recoded ~ age_group_letter_child + pediatric_care_letter_child + highest_parental_education_group + fte_category_18 + duration_until_check_up_non_urgent + duration_until_emergency + waiting_time + duration_check_up, family = quasibinomial(), design = parent_survey_design)

plot(model_2m)

summary(model_2m)
cbind(exp(summary(model_2m)$coef[,1]), exp(confint(model_2m)))

glance(model_2k)
glance(model_2m)
anova(model_2k, model_2m)

```



```{r}
#| warning: false

plot(model_2k)

View(tidy(model_2k, conf.int = TRUE, exponentiate = TRUE) %>% 
  mutate(
    aOR_CI = sprintf("%.2f [%.2f–%.2f]", estimate, conf.low, conf.high)
  ) %>%
  select(term, aOR_CI))



data_included |> select(satisfaction_doctor_recoded, age_group_letter_child, pediatric_care_letter_child, fte_category_18, duration_until_check_up_non_urgent, duration_until_emergency, waiting_time, duration_check_up) |>
  drop_na() |> nrow()

```

### Alternative Figure: Regression Figure

```{r}
#| warning: false

model_summary <- tidy(model_2b, conf.int = TRUE, exponentiate = TRUE)

model_summary <- model_summary |> 
  filter(term !="(Intercept)") |> 
  mutate(aOR = estimate,
         lower_ci = conf.low,
         upper_ci = conf.high) |> 
  select(term, aOR, lower_ci, upper_ci)



table_plot_multinomial_regression <- model_summary |> 
  mutate(term = case_when(
    # Demographic
    term == "sex_letter_child_fsoFemale" ~ "Female",
    term == "child_rankZweites Kind" ~ "'Second child'",
    term == "child_rankDrittes oder jüngeres Kind" ~ "'Third or later child'",
    term == "age_group_letter_childInfancy (0-1)" ~ "bold('Age group')*': 0–1'",
    term == "age_group_letter_childPreschool (2-5)" ~ "'2–5'",
    term == "age_group_letter_childEarly adolescence (12-15)" ~ "'12–15'",
    term == "age_group_letter_childLate adolescence (16-17)" ~ "'16–17'",
    
    term == "household_partnerSingle parent" ~ "'Single parent'",
    term == "nationality_parentsNon-Swiss" ~ "'Non-Swiss'",
    
    # Socioeconomic
    term == "highest_parental_education_groupBerufslehre mit Weiterbildung" ~ "'Further education'",
    term == "highest_parental_education_groupBerufslehre" ~ "'Apprenticeship'",
    term == "highest_parental_education_groupObligatorische Schule" ~ "'Compulsory school'",
    
    term == "swiss_sep_2_quintile2" ~ "'Quintile 2'",
    term == "swiss_sep_2_quintile3" ~ "'Quintile 3'",
    term == "swiss_sep_2_quintile4" ~ "'Quintile 4'",
    term == "swiss_sep_2_quintile5" ~ "'Quintile 5 (high SEP)'",
    
    # Geography/Environment
    term == "urbanizationIntermediär" ~ "Intermediate",
    term == "urbanizationLändlich" ~ "Rural",

    term == "fte_category_18>0.83" ~ "'>0.83'",
    term == "fte_category_18<0.50" ~ "bold('Pediatrician density (FTE/1000 children)')*': <0.50'",
    TRUE ~ term
  ))

# 2. Define Reference Categories and Headers
table_regression_reference <- data.frame(
  class = "variable",
  term = c("bold(Sex)*', ref: Male'", "' '",
           "bold('Birth rank')*', ref: First child'", "'  '",
           "'ref: 6–11'", "'   '",
           "bold('Parents in household')*', ref: Two parents'", "'    '",
           "bold('Nationality of parents')*', ref: Swiss'", "'     '",
           "bold('Highest parental education')*', ref: University'", "'      '",
           "bold('Urbanization')*', ref: Urban'", "'       '",
           "bold('Swiss-SEP')*', ref: Quintile 1 (low SEP)'", "'        '",
           "'ref: 0.50–0.83'"),
  aOR = 1,
  lower_ci = NA,
  upper_ci = NA
)

# 3. Combine and set Factor Levels for Plot Order
table_plot_multinomial_regression <- table_plot_multinomial_regression |> 
  bind_rows(table_regression_reference) |> 
  mutate(term = factor(term,
                       levels = c(
                         # Continuous
                         "'>0.83'", "'ref: 0.50–0.83'", "bold('Pediatrician density (FTE/1000 children)')*': <0.50'",
                         # Geography
                          "'        '", "Rural", "Intermediate", "bold('Urbanization')*', ref: Urban'",
                         # Socioeconomics
                          "'       '", "'Quintile 5 (high SEP)'", "'Quintile 4'", "'Quintile 3'", "'Quintile 2'", "bold('Swiss-SEP')*', ref: Quintile 1 (low SEP)'",
                          "'      '", "'Compulsory school'", "'Apprenticeship'", "'Further education'", "bold('Highest parental education')*', ref: University'",
                         # Child and Houshold Demographics
                          "'     '", "'Non-Swiss'", "bold('Nationality of parents')*', ref: Swiss'",
                          "'    '", "'Single parent'", "bold('Parents in household')*', ref: Two parents'",
                          "'   '", "'16–17'", "'12–15'", "'ref: 6–11'", "'2–5'", "'0–1'", "bold('Age group')*': 0–1'",
                         "'  '", "Female", "bold(Sex)*', ref: Male'",
                         "' '", "'Third or later child'", "'Second child'", "bold('Birth rank')*', ref: First child'"
                       ))) |> 
  # 5. Handle Visibility and Transparency
  mutate(
    hide = factor(if_else(term %in% table_regression_reference$term, "Yes", "No"), levels = c("Yes", "No")),
    transparency = if_else(term %in% c("' '", "'  '", "'   '", "'    '", "'     '", "'      '", "'       '", "'        '"), "transparent", "normal")
  )


table_plot_multinomial_regression <- table_plot_multinomial_regression |> 
  arrange(desc(term)) |> 
  mutate(group = case_when(row_number()<=13 ~ "Demographic factors",
                           row_number()<=30 ~ "Socioeconomic factors",
                           TRUE ~ "Geographic factors"))


```


```{r}
#| warning: false

table_plot_multinomial_regression <- table_plot_multinomial_regression |> 
  mutate(is_out_left = lower_ci < 0.25)


plot_forrest_multinomial <- table_plot_multinomial_regression |>
  ggplot(aes(x = aOR, y = term)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
  geom_vline(xintercept = 0.25, color = "black") +
  geom_vline(xintercept = 4, color = "black") +
  geom_point(aes(alpha = transparency, color = group), size = 1, position = position_dodge(width = 1)) +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci, color = group),
                 height = 0.25, linewidth = 0.25,
                 position = position_dodge(width = 1)) +
  geom_segment(data = filter(table_plot_multinomial_regression, is_out_left == TRUE),
               aes(x = 0.30, xend = 0.25, y = term, yend = term, color = group),
               arrow = arrow(length = unit(0.15, "cm"), type = "closed"),
               linewidth = 0.25,
               position = position_dodge(width = 1), show.legend = FALSE) +
  scale_x_continuous(breaks = c(0.25, 0.5, 1, 2, 4), transform = "log", expand = c(0,0), limits = c(0.25, 5.25)) +
  coord_cartesian(xlim = c(0.25, 5.25), expand = FALSE, clip = "on")+
  scale_y_discrete(labels = function(x) parse(text = x), expand = c(0,0))+
  scale_color_manual(breaks = c("Demographic factors", "Socioeconomic factors", "Geographic factors"), values = c(unibeIce(), unibeRed(), unibeMustard()))+
  scale_alpha_manual(breaks = c("transparent", "normal"), values = c(0, 100), guide = "none")+
  labs(x = "**aOR** (log scale)", y = "") +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.x = element_markdown(size = 8),
        axis.text.y = element_text(size = 8, color = "black", margin = margin(0, 0, 0, 0)),
        axis.text.x = element_text(size = 8, color = "black"),
        legend.position = "bottom",
        legend.direction = "vertical",
        legend.text = element_text(size = 8, color = "black"),
        legend.key.height = unit(0.3, "cm"),
        legend.title = element_blank(),
        plot.margin = margin(t = 0.75, r = 0.7, l = 0.4, b = 0.5, unit = "cm"))

plot_forrest_multinomial

ggsave(plot_forrest_multinomial, filename = here("output", "figures", "plot_forrest_multinomial.svg"), device = "svg", units = "cm", bg = "white", width = 15, height = 16)

```

## Figure 3: Reasons for dissatisfaction


```{r}
#| warning: false

data_included |> 
  select(answered_satisfied_doctor, unsatisfied_doctor_not_my_language, unsatisfied_doctor_no_time, unsatisfied_doctor_my_concerns, unsatisfied_doctor_not_competent, unsatisfied_doctor_not_prepared, unsatisfied_doctor_not_child_respond) |> 
  tbl_summary(
    missing = "always",
    stat = all_categorical() ~ "{n} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    )

parent_survey_design |> as_survey() |> 
  select(unsatisfied_doctor_not_my_language, unsatisfied_doctor_no_time, unsatisfied_doctor_my_concerns, unsatisfied_doctor_not_competent, unsatisfied_doctor_not_prepared, unsatisfied_doctor_not_child_respond) |> 
  tbl_svysummary(
    missing = "always",
    stat = all_categorical() ~ "{n_unweighted} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 1, scale = 100))

tbl_unsatisfied_doctor <- parent_survey_design |> as_survey() |> 
  select(unsatisfied_doctor_not_my_language, unsatisfied_doctor_no_time, unsatisfied_doctor_my_concerns, unsatisfied_doctor_not_competent, unsatisfied_doctor_not_prepared, unsatisfied_doctor_not_child_respond) |> 
  tbl_svysummary(
    missing = "always",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))



data_included |> 
  select(answered_satisfied_practice, unsatisfied_practice_far_away, unsatisfied_practice_few_appointments, unsatisfied_practice_not_open, unsatisfied_practice_not_child_friendly, unsatisfied_practice_personnel_unfriendly) |> 
  tbl_summary(
    missing = "always",
    stat = all_categorical() ~ "{n} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    )

parent_survey_design |> as_survey() |> 
  select(unsatisfied_practice_far_away, unsatisfied_practice_few_appointments, unsatisfied_practice_not_open, unsatisfied_practice_not_child_friendly, unsatisfied_practice_personnel_unfriendly) |> 
  tbl_svysummary(
    missing = "always",
    stat = all_categorical() ~ "{n_unweighted} ({p})",
    digits = list(everything() ~ 0),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 0, scale = 100))


tbl_unsatisfied_practice <- parent_survey_design |> as_survey() |> 
  select(unsatisfied_practice_far_away, unsatisfied_practice_few_appointments, unsatisfied_practice_not_open, unsatisfied_practice_not_child_friendly, unsatisfied_practice_personnel_unfriendly) |> 
  tbl_svysummary(
    missing = "always",
    digits = list(everything() ~ 5),
    missing_stat = "{N_miss} ({p_miss})"
    ) |> 
  add_ci(method = all_categorical() ~ "svyprop",
         style_fun = all_categorical() ~ label_style_sigfig(digits = 5, scale = 100))



```


```{r}
#| warning: false

data_unsatisfied_doctor <- tbl_unsatisfied_doctor |> 
  as_tibble() |> 
  filter(`**Characteristic**` != "Unknown") |> 
  transmute(
    Factor = `**Characteristic**`,
    n_perc = `**N = 8,651**`,
    ci_text = `**95% CI**`
  ) |> 
  mutate(
    yes_count = as.numeric(str_remove_all(str_extract(n_perc, "^[0-9,]+"), ",")),
    yes_proportion = str_extract(n_perc, "\\(([^\\)]+)\\)") %>%
                     str_remove_all("[^0-9\\.]") %>%
                     as.numeric() / 100,
    yes_ci_lower = str_extract(ci_text, "^[0-9\\.]+") %>% as.numeric() / 100,
    yes_ci_upper = str_extract(ci_text, "[0-9\\.]+(?=%?$)") %>% as.numeric() / 100) |> 
  select(Factor, yes_count, yes_proportion, yes_ci_lower, yes_ci_upper)


data_unsatisfied_doctor <- data_unsatisfied_doctor |> 
  mutate(Factor = factor(Factor, levels = c("unsatisfied_doctor_not_my_language",  "unsatisfied_doctor_not_competent", "unsatisfied_doctor_not_prepared", "unsatisfied_doctor_my_concerns", "unsatisfied_doctor_not_child_respond", "unsatisfied_doctor_no_time"), labels = c("Not my mother language", "Not competent", "Not prepared", "Not adressing my concerns", "Not connecting with my child", "Not enough time")))

plot_unsatisfied_doctor <- data_unsatisfied_doctor |>
  ggplot(aes(y = Factor, x = yes_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(x = yes_proportion/2, label = paste0(round(yes_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(9))+
  geom_errorbarh(aes(xmin = yes_ci_lower, xmax = yes_ci_upper), height = 0.25)+
  scale_x_continuous(labels = percent, limits = c(0, 0.5))+
  theme_minimal()+
  ggtitle("Doctor's characteristics")+
  xlab("Parents (%) reporting this reason for unsatisfaction")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color = "black"),
        plot.title = element_text(size = 12, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"))

plot_unsatisfied_doctor


data_unsatisfied_practice <- tbl_unsatisfied_practice |> 
  as_tibble() |> 
  filter(`**Characteristic**` != "Unknown") |> 
  transmute(
    Factor = `**Characteristic**`,
    n_perc = `**N = 8,651**`,
    ci_text = `**95% CI**`
  ) |> 
  mutate(
    yes_count = as.numeric(str_remove_all(str_extract(n_perc, "^[0-9,]+"), ",")),
    yes_proportion = str_extract(n_perc, "\\(([^\\)]+)\\)") %>%
                     str_remove_all("[^0-9\\.]") %>%
                     as.numeric() / 100,
    yes_ci_lower = str_extract(ci_text, "^[0-9\\.]+") %>% as.numeric() / 100,
    yes_ci_upper = str_extract(ci_text, "[0-9\\.]+(?=%?$)") %>% as.numeric() / 100) |> 
  select(Factor, yes_count, yes_proportion, yes_ci_lower, yes_ci_upper)


data_unsatisfied_practice <- data_unsatisfied_practice |> 
  mutate(Factor = factor(Factor, levels = c("unsatisfied_practice_not_child_friendly", "unsatisfied_practice_personnel_unfriendly", "unsatisfied_practice_far_away", "unsatisfied_practice_not_open",  "unsatisfied_practice_few_appointments"), labels = c("Not child friendly", "Unfriendly personnel", "Far away from home", "Not open when I have time", "Few appointments available")))

plot_unsatisfied_practice <- data_unsatisfied_practice |>
  ggplot(aes(y = Factor, x = yes_proportion))+
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(x = yes_proportion/2, label = paste0(round(yes_proportion*100, digits = 0), "%")), color = "white", size = ggtext_size(9))+
  geom_errorbarh(aes(xmin = yes_ci_lower, xmax = yes_ci_upper), height = 0.25)+
  scale_x_continuous(labels = percent, limits = c(0, 0.5))+
  theme_minimal()+
  ggtitle("Practice's characteristics")+
  xlab("Parents (%) reporting this reason for unsatisfaction")+
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(color = "black"),
        plot.title = element_text(size = 12, color = "black"),
        plot.title.position = "plot",
        axis.title.y = element_blank(),
        axis.text = element_text(size = 10, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"))

plot_unsatisfied_practice

plot_figure_unsatisfaction <- plot_grid(plot_unsatisfied_doctor+theme(axis.title.x = element_blank()),
                           plot_unsatisfied_practice,
                           ncol = 1,
                           align = "hv")

plot_figure_unsatisfaction

ggsave(filename=file.path(here("output","figures","plot_figure_unsatisfaction.svg")),plot_figure_unsatisfaction,device=svg,units="cm", height=10, width=18)

```




